Improve Taxonomy Assignment

### 2022-02-10 reports/rmarkdown/01_taxonomy_improved.Rmd
Clean up + minor changes

---
title: "`r params$project_title`"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
params:
  organisation: Karolinska Institutet
  pi_mail: krisina.broliden@ki.se
  pi_name: Kristina Broliden
  project_title: Broliden_5325
---

@@

@@

```{r Get ASV and tax tables, message=FALSE}
paths_p <- c('../../data/phyloseq_boston_r1.RDS',   # CVL V3
             '../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../data/phyloseq_Sthlm.RDS')       # CVL V2, only v4 region

@@

#### ASV with all controls and replicate samples removed ####
ASV_names <- c("ASV_CVL_V2_B1", "ASV_CVL_V3", "ASV_tissue_B1", 
               "ASV_CVL_V2_B2", "ASV_tissue_B2", "ASV_CVL_V2_C" )
ASV_list <- map(ASV, ~ .x %>%
                  filter(grepl("yes", .$Include)) %>%
                  group_split(Sample_type, Visit, .keep = T)
            ) %>%
            flatten() %>%
            set_names(ASV_names) %>%
            map(., ~ .x %>%
                select(Sequence, ID, Reads) %>%
                pivot_wider(., ,names_from=ID, values_from=Reads) %>%
                left_join(., new_taxtable, by="Sequence") 
                )

@@

>>>>

---
title: "Improve Taxonomy Assignment"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
---

@@

#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown")
```

@@

```{r Get ASV and tax tables, message=FALSE}
paths_p <- c('../../data/phyloseq_boston_r1.RDS',   # CVL V3 (2 replicates of one tissue + 27 CVLv2)
             '../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../data/phyloseq_Sthlm.RDS')       # CVL V2, only v4 region

@@

#### ASV with all controls and replicate samples removed ####
ASV_names <- c("ASV_CVL_V2_B1", "ASV_CVL_V3_B1", "ASV_tissue_V3_B1", 
               "ASV_CVL_V2_B2", "ASV_tissue_V3_B2", "ASV_CVL_V2_S" )
ASV_list <- map(ASV, ~ .x %>%
                  filter(grepl("yes", .$Include)) %>%
                  group_split(Sample_type, Visit, .keep = T)
            ) %>%
            flatten() %>%
            set_names(ASV_names) %>%
            map(., ~ .x %>%
                select(Sequence, ID, Reads) %>%
                pivot_wider(., ,names_from=ID, values_from=Reads) %>%
                left_join(., new_taxtable, by="Sequence") 
                )

@@

saveRDS(ASV, paste0(PATH,"results/","ASV_wCtrl_long_format.RDS"))
```
